---
title: "p8105_hw5_cgd2137"
author: "Carolina Downie"
date: "11/1/2017"
output: html_document
---

```{r loading packages}
library(tidyverse)
library(rvest)
library(httr)
library(forcats)
library(stringr)
library(janitor)
library(haven)
library(stringr)
library(forcats)
```

#Problem 1: 
Using the State of New York API, read the complete dataset using functions in httr. By default, the API will return only the first 1000 entries, so using the GET option query = list($limit= 2000) in your request will be useful.

```{r loading and cleaning New York subway data}
nyc_subway <- GET("https://data.ny.gov/resource/hvwh-qtfg.json", query = list("$limit" = 2000)) %>% 
  content("text") %>%
  jsonlite::fromJSON() %>%
  select(station_name, north_south_street, east_west_street, entrance_latitude, entrance_longitude, corner)
```

Make a plot showing the number of entrances for each subway station. Restrict your plot to stations that have more than 10 entrances, and order stations according to the number of entrances.

```{r number of entrances for each subway station}
nyc_subway %>% group_by(station_name) %>%
  mutate(num_entrances = n()) %>%
  filter(num_entrances > 10) %>%
  ggplot(aes(x = fct_reorder(station_name, num_entrances), y = num_entrances)) + 
    geom_point() + labs(
    title = "Number of entrances for each subway station",
    x = "Subway station",
    y = "Number of entrances") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
  

```

Overall (not only in stations that have more than 10 entrances), how many subway station names contain the abbreviation “St”? How many end with “St”?

```{r subway stations containing St}

nyc_subway_contains_st<-nyc_subway %>% filter(str_detect(station_name, "St")) 
  
```

There are `r length(unique(nyc_subway_contains_st$station_name))` subway stations containing "St" in their name. 

```{r subway statins ending in St}
nyc_subway_ends_St<-nyc_subway_contains_st %>% 
  pull(station_name) %>% 
  str_locate(., "St") %>% 
  data.frame() %>% 
  cbind(., nyc_subway_contains_st) %>%
  filter(end == str_length(station_name))

length(unique(nyc_subway_ends_St$station_name))
```

There are `r length(unique(nyc_subway_ends_St$station_name))` subway stations with names ending in "St". 